MGRFE: multilayer recursive feature elimination based on an embedded genetic algorithm for cancer classification

### 2019-05-27 MGRFE-TCBB-2019-05-27/MGRFE-tcbb.tex
Complete the round 2. Be brave.

	\IEEEtitleabstractindextext{
	\begin{abstract}
	\justifying
	Microarray gene expression data have become a topic of great interest for cancer classification and for further research in the field of bioinformatics. Nonetheless, due to the ``large \(p\), small \(n\)'' paradigm of limited biosamples and high-dimensional data, gene selection is becoming a demanding task, which is aimed at selecting a minimal number of discriminatory genes associated closely with a phenotype. Feature or gene selection is still a challenging problem owing to its nondeterministic polynomial time complexity and thus most of the existing feature selection algorithms utilize heuristic rules.
	A multilayer recursive feature elimination method based on an embedded integer-coded genetic algorithm with a dynamic-length chromosome, MGRFE, is proposed here, which is aimed at selecting the gene combination with minimal size and maximal information. On the basis of 19 benchmark microarray datasets including multiclass and imbalanced datasets, MGRFE outperforms state-of-the-art feature selection algorithms with better cancer classification accuracy and a smaller selected gene number. MGRFE could be regarded as a promising feature selection method for high-dimensional datasets especially gene expression data. Moreover, the genes selected by MGRFE have significant biological relevance to cancer phenotypes. The source code of our proposed algorithm and all the 19 datasets used in this paper are available at \url{https://github.com/Pengeace/MGRFE-GaRFE}.
	\end{abstract}

@@

	Filter algorithms generally evaluate features according to the inherent characteristic of a dataset, then rank all the features and preserve only an optimal subset of the original features. Up to now, lots of filter algorithms have been designed, such as the methods based on the \textit{t}-test \cite{W23}, $\chi^2$ test \cite{W21}, mutual information \cite{W22}, maximal information coefficient (MIC) \cite{W25}, and signal-to-noise ratio \cite{W24}. The \textit{t}-test is the frequently used and efficient statistical approach to detecting differentially expressed genes in microarray analysis \cite{RN413, RN414, RN421, RN417, RN418, RN419, RN416}. MIC is an information theory-based measurement for capturing a wide range of associations, which has shown excellent performance on detecting novel associations in large datasets \cite{W8}. The recent study of McTwo \cite{W16}, which is based on MIC for selection of a gene subset in a microarray data, has outperformed most of existing algorithms. In addition, MIC may offer more convenience in dealing with multiclass datasets. Hence, the \textit{t}-test and MIC are practicable and qualified approaches for selecting statistically significant discriminative genes and thus are mostly used in the feature preprocessing stage to generate a candidate gene set in the analysis of microarray. Because there is no classification algorithm involved in the filter algorithm, its computational speed is high and suitable for large datasets. On the other hand, the filter techniques for gene feature selection also have some limitations. First, filter methods are likely to add redundant features into the chosen subsets, which will lead to inaccessibility of optimal results. Second, genes in the cell interact with other genes to perform a certain biological function, but the filter methods select genes individually rather than gene combinations \cite{P34}. Third, the features top-ranked by a filter algorithm are not always the best features for classification \cite{W16}.

	Wrapper algorithms usually employ classification models and contain heuristic rules to select feature subsets guided by the classification performance on the feature subsets being used, which are usually superior to filter algorithms but more time-consuming. A variety of wrapper algorithms have emerged involving simulated annealing, randomized hill climbing \cite{W26}, regularized random forest (RRF) \cite{W11}, particle swarm optimization (PSO) \cite{W12,W10}, and genetic algorithm (GA) \cite{W13}. With the rapid development of heuristic rules and evolutionary strategies commonly present in wrapper techniques, various swarm intelligence algorithms have been applied to the optimization of feature selection. Kar \emph{et~al.} have proposed a particle swarm optimization method based on adaptive K-nearest neighborhood (KNN) to identify a minimum meaningful gene subset \cite{W15}. Moosa \emph{et~al.} have presented a modified artificial bee colony algorithm (ABC) to select a minimum number of genes with high predictive accuracy for cancer classification \cite{P32}. Oreski \emph{et~al.} have designed a hybrid GA with neural networks to identify an optimal feature subset with high classification accuracy and scalability for credit risk assessment \cite{W17}. Jung and Zscheischler have described a guided hybrid GA to minimize the number of cost function evaluations \cite{W18}. Nevertheless, all these feature selection methods based on swarm intelligence algorithms use the binary encoding method and lack an explicit reduction in the feature number. The feature number only changes in the randomized evolution operation like mutation and crossover. Thus, these methods lack the precise control over the gene features in the individuals and can not explicitly remove genes to decrease the feature number. Meanwhile, it has been verified that only a minimal number of informative genes is enough for effective diagnosis of different phenotypes in microarray gene datasets \cite{P1,W16,P32,P33}. The feature selection using binary encoding has three main shortcomings in finding an optimal gene combination: (1) The fixed chromosome length for the encoding length must be equal to the gene range to represent all the genes. This arrangement can result in impossibility of the explicit reduction in the gene number and unnecessary space occupation when there are only several 1s among lots of 0s. (2) There are different numbers of actual existing genes in different individuals. Because there are different numbers of 1s, the actual number of genes varies among individuals and cannot be controlled precisely. (3) The convergence speed is usually low and the time cost is high to generate the minimal informative gene combination. 
	The sizes of the optimal gene combinations in most of datasets are below 10. The evolution-based feature selection algorithms using binary encoding lack of an explicit feature reduction mechanism, which results in low probability and high time cost to generate the optimal minimal gene combination among the several thousand to tens of thousands of genes in each dataset.
	Recursive feature elimination (RFE) is a popular strategy that yields an explicit recursive feature reduction by removing features with the least weights \cite{W7,P1,P2,P27}.

@@

	A multilayer recursive feature elimination method with an embedded integer-coded genetic algorithm, MGRFE, is proposed here, which can be categorized into a hybrid algorithm. On the one hand, MGRFE uses the \textit{t}-test and MIC in the search space reduction stage to generate a candidate gene set. On the other hand, MGRFE combines the advantages of both evolution calculation of GA and the explicit feature elimination of RFE to achieve the minimum discriminative gene subset with optimal classification ability.
	To validate the performance of the proposed method, we comprehensively compared our proposed MGRFE with the feature selection methods from 20 representative studies on 19 benchmark gene expression datasets including multiclass and imbalanced datasets. The comparison results show that our method outperforms most of state-of-the-art feature selection algorithms. MGRFE can select a smaller gene subset but yield the same or higher classification accuracy than other algorithms. Furthermore, the specific biomedical relevance of the selected genes to the related cancer phenotypes has also been verified by text mining. The whole work flow of this study is presented in Fig. \ref{Fig:MGRFE_whole}.

	\begin{figure*}[!htbp]
		\centering
		\includegraphics[width=0.6\textwidth]{pictures/MGRFE-whole.pdf}
		\caption{A flowchart of the whole MGRFE procedure in this study.}
		\label{Fig:MGRFE_whole}
	\end{figure*}

@@

	As shown in Fig. \ref {Fig:MGRFE_flowchart}, the proposed MGRFE is divided into three stages, which are (1) Search space reduction; (2) Precise wrapper search and (3) Multiple k-fold cross-validation (CV). MGRFE is a multilayer iterative feature selection method with GaRFE acting as the feature selection unit in every layer. GaRFE is a recursive feature elimination process including embedded GA. The Pseudocodes 1, 2 and 3 in Supplementary Material provide the pseudocodes of the processes MGRFE, GaRFE and embedded GA.

	\begin{figure*}[t]
		\centering
		\includegraphics[width=0.87\textwidth]{pictures/MGRFE-flowchart.pdf}
		\caption{The flowchart of MGRFE, which is divided into 3 stages: search space reduction, precise wrapper search, and multiple k-fold CV. Stage 2 is the core of MGRFE, which includes two key processes: GaRFE and embedded modified GA.}
		\label{Fig:MGRFE_flowchart}
	\end{figure*}

@@

	At Stage 2, we search the candidate gene set obtained from Stage 1 and compute the optimal gene combinations for further selection at Stage 3. MGRFE is a multilayer iterative feature selection method and its selection unit in each layer is a GaRFE process. GaRFE, the inverted triangle in MGRFE as shown in Fig. \ref{Fig:MGRFE_whole}, is the recursive feature elimination process with every stair being embedded GA. Embedded GA is the integer-coded genetic algorithm with a dynamic-length chromosome. The key feature of MGRFE is GaRFE in each layer, in which embedded GA is responsible for generating optimal gene combinations, and the RFE process is responsible for cutting down the gene number. Therefore, our method can find gene combinations with both significantly reduced sizes and excellent classification performance.

@@

	In our method, the modified GA using variable-length integer-coded chromosome is embedded in the RFE process as each stair in the inverted triangle of GaRFE. The embedded GA includes the following steps. First, we initialize the GA population by a certain amount of individuals representing gene combinations with the same sizes. Then, we perform fitness calculation and genetic operators including mutation, crossover, and selection until the stopping criterion is satisfied. In the end, we return the best individuals that represent the best gene combinations to GaRFE. The stopping criterion of embedded GA is iteration time, which is set to 1 to 3.

@@

	A truncation selection method is used as the selection operator in embedded GA \cite{P37}, which simply ranks all individuals and selects the top ones to form the next generation. The mutation and crossover operators for generating new individuals are adjusted to adapt to the variable-length integer-encoding technique. One main challenge that should be addressed in these two processes is avoidance of duplicated genes in every individual, which leads to the decline of the number of actual existing genes. Based on our encoding technique, the mutation operation for an individual is randomly changing some genes to others. It should be ensured that new genes do not exist in this individual previously to avoid repetitions. Crossover in embedded GA also involves single-point crossover which is the most widely used crossover method in binary encoding. Specifically, a random position is selected in the chromosome, and two parent individuals split themselves at this crossover point and then exchange chromosome tails to generate children individuals. After the crossover, the potential duplicate genes in the children individuals are replaced with other genes from their parents to avoid decreasing the gene number. Fitness (\(F\)) of an individual is defined in Equation (\ref{eq:2}):
	{
		\scriptsize
		\begin{eqnarray}\label{eq:2}
		F = \left\{
		\begin{array}{cl}
		Acc & {,{balanced\ dataset}}\\
		\alpha Acc + (1-\alpha)Avc & {,{imbalanced\ dataset}}\\
		\end{array} \right.
		\end{eqnarray}
	}
	, where \(\alpha\) is an adjustment coefficient to deal with the imbalanced datasets. For imbalanced datasets, fitness defined as \(\alpha Acc +(1-\alpha)Avc\) can adjust the trend of predicting samples as abundant classes for \(Avc = (Sn + Sp) \big/ 2\) takes the correct prediction proportion of both sample classes into consideration. In our experiments, we take \(\alpha\) 0.6 for imbalanced datasets. For balanced datasets, \(F\) is simply defined as \(Acc\). \(F\) is calculated by 5-fold CV, and the employed classifier is Naive Bayes classifier (NBayes) \cite{P35}. We sort different GA individuals based on two metrics, \(F\) and gene number. The individual with higher \(F\) is superior. For two individuals with the same \(F\) values, the one with a smaller gene number is superior. MGRFE and GaRFE also use the above-mentioned sorting rule to rank different gene combinations.

@@

	GaRFE as shown in Fig. \ref {Fig:MGRFE_flowchart} is designed as an explicit recursive feature elimination process with embedded GA to find minimal discriminatory gene combinations. First, we randomly generate the initial GA population based on a certain candidate gene set and chromosome length. Then, we implement a chromosome length drop and a GA run in turns until the chromosome length in GA drops to 1. Finally, we sort the optimal gene combinations from all GA runs and then return the overall top-ranked gene combinations to MGRFE. The chromosome length drop means that every individual in the current GA population randomly discards the same number of genes to generate the new GA population for the next run. The number of discarded genes between two GA runs, the RFE step, is set from 1 to 3 according to the current chromosome length. A larger decline step is set for larger chromosome length to avoid time cost and a smaller decline step set for smaller chromosome length to do precise searching.

@@

	MGRFE is designed as a multilayer iterative feature selection method with the selection unit in each layer being GaRFE. In every iteration layer, the GaRFE processes analyze the current candidate gene set and return their obtained optimal gene combinations. Then the candidate gene set is reduced and subjected to the next layer of iterative selection. The candidate gene set used by the first layer of MGRFE is from the search space reduction stage. After each iteration layer, all optimal gene combinations in MGRFE will be sorted and the top-ranked ones will form the updated reduced candidate gene set. After the specified layers of iteration, MGRFE sorts all the optimal gene combinations and provides the top-ranked gene combinations for Stage 3 to execute further validation.

@@

	In this section, our proposed MGRFE is comprehensively compared with the state-of-the-art algorithms of gene selection on 19 benchmark datasets.
	Additionally, the biological verification of the selected genes is discussed.

@@

	The results of MGRFE on Dataset One including 17 binary datasets are given in Table \ref{Tab:RST all index}, where six measurements calculated by 5-fold CV and the \textit{t}-test and MIC-based gene rankings are listed. For 17 datasets, \(Acc\) values are all above 0.9 within 10 genes. Moreover, for 8 of 17 datasets (DLBCL, Leuk, ALL1, Lym, Adeno, Gas, Gas2, and Stroke), \(Acc\) reached 1.0 with gene number less than 5. MGRFE also show the strong robustness in dealing with imbalanced datasets like DLBCL, Colon, Leuk, ALL1, ALL4, and CNS, for which \(Sn\), \(Sp\), \(Avc\), \(MCC\), and \(AUC\) are all above 0.95 without being influenced by the data imbalance. 
	According to the \textit{t}-test and MIC-based gene ranking, the best gene feature subset is not always the highest-ranked features in the filter method, thus the filter algorithm alone cannot generate the optimal feature combination.
	It could be noted that the relative positions of selected genes in the two ranking methods are consistent on most datasets. The top-ranked genes in the \textit{t}-test are also top-ranked in the MIC sorting (e.g. the selected gene on ALL1 is the top one in both \textit{t}-test and MIC ranking). For 5 of 17 datasets, the top one gene  according to the \textit{t}-test appeared in the final selected gene subsets. Generally, the selected informative genes are top-ranked by the \textit{t}-test and MIC methods. Therefore, the filter techniques are qualified for the search space reduction stage. Moreover, MGRFE achieves stable classification performance in 10 repetitions of 10-fold CV as depicted in Fig. \ref{Fig:CV1}. Besides, we also validated the selected gene features of Leuk, Gas1 and Gas2 on independent datasets in the "S8" section of Supplementary Material.

@@

	McTwo \cite{W16} thoroughly tested all the datasets in Dataset One and demonstrated satisfactory performance. Here, we present the performance comparison between McTwo and MGRFE. Table \ref{Tab:CMP McTwo RST} lists the overall maximal \(Acc\) and numbers of selected genes on total 17 datasets for MGRFE and McTwo. For a more intuitive comparison, Fig. \ref{Fig:CMP McTwo} offers the line chart of maximal \(Acc\) achieved by the two algorithms on 17 datasets, where MGRFE obviously outperforms McTwo with a higher \(Acc\) line. On five datasets ALL2, ALL3, ALL4, Stroke and CNS, MGRFE achieves distinctly better classification performance than McTwo with relatively more genes. For a fairer and more specific comparison, the \(Acc\) values of the two algorithms are listed when the gene number of MGRFE is equal to McTwo as shown in Table \ref{Tab:same gene num}. The results indicate that MGRFE still outperforms McTwo. Nonetheless, the \(Acc\) values associated with the usage of the gene numbers fall behind our optimal \(Acc\) values on these datasets obviously. Thus, MGRFE selected somewhat more genes to achieve the optimal results.

	\begin{figure*}[ht]
		\centering
		\includegraphics[width=0.72\textwidth]{pictures/CMP-McTwo.pdf}
		\caption{The line plots of overall maximal accuracy for MGRFE and McTwo on 17 datasets in Dataset One.}
		\label{Fig:CMP McTwo}
	\end{figure*}

@@

	Here we present the results of MGRFE on Dataset Two including three benchmark datasets, where two datasets are multiclass datasets. MGRFE selects five, two, and three genes in SRBCT, ALL\_AML, and MLL respectively and the overall maximal \(Acc\)s are all 1.0 in 5-fold CV. Fig. \ref{Fig:3 RFE on benchmarks} offers three instances of GaRFE processes in the first layer of MGRFE for these datasets, where we can notice that the \(Acc\) values of the best GA individuals are kept at 1.0 in the majority of gene number ranges and begin to drop only when the gene number is significantly reduced. We also carried out 10 repetitions of 10-fold CV to further validate the final selected gene combinations in Dataset Two as shown in Fig. \ref{Fig:CV2}. The mean of \(Acc\)s for SRBCT, ALL\_AML, and MLL are 1.0, 0.982, and 0.997, respectively, with standard deviations being 0.0, 0.008, and 0.006. These data confirm that MGRFE has high classification stability.

	\begin{figure*}[!htbp]
		\begin{minipage}[t]{0.3\textwidth}
			\centering
			\includegraphics[height=1.65in]{pictures/SRBCT-RFE.pdf}
		\end{minipage}
		\begin{minipage}[t]{0.3\textwidth}
			\centering
			\includegraphics[height=1.65in]{pictures/ALLAML-RFE.pdf}
		\end{minipage}
		\begin{minipage}[t]{0.3\textwidth}
			\centering
			\includegraphics[height=1.65in]{pictures/MLL-RFE.pdf}
		\end{minipage}
		\caption{Three typical GaRFE processes on the three benchmark datasets from Dataset Two.}
		\label{Fig:3 RFE on benchmarks}
	\end{figure*}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.47\textwidth]{pictures/CV2.pdf}
		\caption{The distribution of $Acc$ values in 10-time 10-fold CV for the selected gene combinations in Dataset Two.}
		\label{Fig:CV2}
	\end{figure}

@@

	\begin{table*}[htbp]
		\centering
		\caption{Performance comparison among the methods on the MLL dataset}
		\label{Tab:MLL RST}
		\resizebox{0.9\textwidth}{!}{
			\begin{tabular}{lllllllllllll}
				\toprule
				Experiments & Methods & \multicolumn{4}{l}{Genes} & \multicolumn{4}{l}{CV $Acc$(\%)} & Train $Acc$(\%) & Test $Acc$(\%) \\
				\midrule

>>>>

	\IEEEtitleabstractindextext{
	\begin{abstract}
	\justifying
	Microarray gene expression data have become a topic of great interest for cancer classification and for further research in the field of bioinformatics. Nonetheless, due to the ``large \(p\), small \(n\)'' paradigm of limited biosamples and high-dimensional data, gene selection is becoming a demanding task, which is aimed at selecting a minimal number of discriminatory genes associated closely with a phenotype. Feature or gene selection is still a challenging problem owing to its nondeterministic polynomial time complexity and thus most of the existing feature selection algorithms utilize heuristic rules.
	A multilayer recursive feature elimination method based on an embedded integer-coded genetic algorithm, MGRFE, is proposed here, which is aimed at selecting the gene combination with minimal size and maximal information. On the basis of 19 benchmark microarray datasets including multiclass and imbalanced datasets, MGRFE outperforms state-of-the-art feature selection algorithms with better cancer classification accuracy and a smaller selected gene number. MGRFE could be regarded as a promising feature selection method for high-dimensional datasets especially gene expression data. Moreover, the genes selected by MGRFE have close biological relevance to cancer phenotypes. The source code of our proposed algorithm and all the 19 datasets used in this paper are available at \url{https://github.com/Pengeace/MGRFE-GaRFE}.
	\end{abstract}

@@

	Filter algorithms generally evaluate features according to the inherent characteristic of a dataset, then rank all the features and preserve only an optimal subset of the original features. Up to now, lots of filter algorithms have been designed, such as the methods based on the \textit{t}-test \cite{W23}, $\chi^2$ test \cite{W21}, mutual information \cite{W22}, maximal information coefficient (MIC) \cite{W25}, and signal-to-noise ratio \cite{W24}. The \textit{t}-test is the frequently used and efficient statistical approach to detecting differentially expressed genes in microarray analysis \cite{RN413, RN414, RN421, RN417, RN418, RN419, RN416}. MIC is an information theory-based measurement for capturing a wide range of associations, which has shown excellent performance on detecting novel associations in large datasets \cite{W8}. The recent study of McTwo \cite{W16}, which is based on MIC for selection of a gene subset in a microarray data, has outperformed most of existing algorithms. In addition, MIC may offer more convenience in dealing with multiclass datasets. Hence, the \textit{t}-test and MIC are practicable and qualified approaches for selecting statistically significant discriminative genes and thus are mostly used in the feature preprocessing stage to generate a candidate gene set in the analysis of microarray. Because there is no classification algorithm involved in the filter algorithm, its computational speed is high and suitable for large datasets. On the other hand, the filter techniques for gene feature selection also have some limitations. First, filter methods are likely to add redundant features into the chosen subsets, which will lead to inaccessibility of optimal results. Second, the mutual information between features is ignored for the implicit orthogonality assumption of features \cite{P1}. Third, the features top-ranked by a filter algorithm are not always the best features for classification \cite{W16}.

	Wrapper algorithms usually employ classification models and contain heuristic rules to select feature subsets guided by the classification performance on the feature subsets being used, which are usually superior to filter algorithms but more time-consuming. A variety of wrapper algorithms have emerged involving simulated annealing, randomized hill climbing \cite{W26}, regularized random forest (RRF) \cite{W11}, particle swarm optimization (PSO) \cite{W12,W10}, and genetic algorithm (GA) \cite{W13}. With the rapid development of heuristic rules and evolutionary strategies commonly present in wrapper techniques, various swarm intelligence algorithms have been applied to the optimization of feature selection. Kar \emph{et~al.} have proposed a particle swarm optimization method based on adaptive K-nearest neighborhood (KNN) to identify a minimum meaningful gene subset \cite{W15}. Moosa \emph{et~al.} have presented a modified artificial bee colony algorithm (ABC) to select a minimum number of genes with high predictive accuracy for cancer classification \cite{P32}. Oreski \emph{et~al.} have designed a hybrid GA with neural networks to identify an optimal feature subset with high classification accuracy and scalability for credit risk assessment \cite{W17}. Jung and Zscheischler have described a guided hybrid GA to minimize the number of cost function evaluations \cite{W18}. Nevertheless, all these feature selection methods based on swarm intelligence algorithms use the binary encoding method and lack an explicit reduction in the feature number. The feature number only changes in the randomized evolution operation like mutation and crossover. Thus, these methods lack the precise control over the gene features in the individuals and can not explicitly remove genes to decrease the feature number. Meanwhile, it has been verified that only a minimal number of informative genes is enough for effective diagnosis of different phenotypes in microarray gene datasets \cite{P1,W16,P32,P33}. The feature selection using binary encoding has three main shortcomings in finding an optimal gene combination: (1) The fixed chromosome length for the encoding length must be equal to the gene range to represent all the genes. This arrangement can result in impossibility of the explicit reduction in the gene number and unnecessary space occupation when there are only several 1s among lots of 0s. (2) There are different numbers of actual existing genes in different individuals. Because there are different numbers of 1s, the actual number of genes varies among individuals and cannot be controlled precisely. (3) The convergence speed is usually low and the time cost is high to generate the minimal informative gene combination. 
	The sizes of the optimal gene combinations in most of datasets are usually below 10. The evolution-based feature selection algorithms using binary encoding lack of an explicit feature reduction mechanism, which results in low probability and high time cost to generate the optimal minimal gene combination among the several thousand to tens of thousands of genes in each dataset.
	Recursive feature elimination (RFE) is a popular strategy that yields an explicit recursive feature reduction by recursively removing features with the least weights \cite{W7,P1,P2,P27}.

@@

	A multilayer recursive feature elimination method with an embedded integer-coded genetic algorithm, MGRFE, is proposed here, which can be categorized into a hybrid algorithm. On the one hand, MGRFE uses the \textit{t}-test and MIC to obviously reduce the feature range and generate a candidate feature set. On the other hand, MGRFE combines the advantages of both evolution calculation of GA and the explicit feature elimination of RFE to achieve the minimum discriminative gene subset with optimal classification ability.
	To validate the performance of the proposed method, we performed comprehensive experiments on 19 benchmark gene expression datasets including multiclass and imbalanced datasets and   compared the performance with other various feature selection methods. 
	The comparison results show that our method outperforms most of state-of-the-art feature selection algorithms for selecting a smaller gene subset but yielding the same or higher classification accuracy. By validation experiments on independent datasets, the generalization ability of selected feature subset by MGRFE is verified. Furthermore, the specific biomedical relevance of the selected genes to the related cancer phenotypes has also been confirmed by text mining in Pubmed. The whole work flow of this study is presented in Fig. \ref{Fig:MGRFE_whole}.

	\begin{figure*}[!htbp]
		\centering
		\includegraphics[width=0.57\textwidth]{pictures/MGRFE-whole.pdf}
		\caption{A flowchart of the whole MGRFE procedure in this study.}
		\label{Fig:MGRFE_whole}
	\end{figure*}

@@

	As shown in Fig. \ref {Fig:MGRFE_flowchart}, the proposed MGRFE is divided into three stages, which are (1) Search space reduction; (2) Precise wrapper search and (3) Multiple k-fold cross-validation (CV). MGRFE is a multilayer iterative feature selection method with GA-RFE acting as the feature selection unit in every layer. GA-RFE is a recursive feature elimination process including embedded GA. The Pseudocodes 1, 2 and 3 in Supplementary Material provide the pseudocodes of the processes MGRFE, GA-RFE and embedded GA.

	\begin{figure*}[t]
		\centering
		\includegraphics[width=0.87\textwidth]{pictures/MGRFE-flowchart.pdf}
		\caption{The flowchart of MGRFE, which is divided into 3 stages: search space reduction, precise wrapper search, and multiple k-fold CV. Stage 2 is the core of MGRFE, which includes two key processes: GA-RFE and embedded modified GA.}
		\label{Fig:MGRFE_flowchart}
	\end{figure*}

@@

	At Stage 2, we search the candidate gene set obtained from Stage 1 and compute the optimal gene combinations for further selection at Stage 3. MGRFE is a multilayer iterative feature selection method and its selection unit in each layer is a GA-RFE process. GA-RFE, the inverted triangle in MGRFE as shown in Fig. \ref{Fig:MGRFE_whole}, is the recursive feature elimination process with every stair being embedded GA. Embedded GA is the integer-coded genetic algorithm with a dynamic-length chromosome. The key feature of MGRFE is GA-RFE in each layer, in which embedded GA is responsible for generating optimal gene combinations, and the RFE process is responsible for cutting down the gene number. Therefore, our method can find gene combinations with both significantly reduced sizes and excellent classification performance.

@@

	In our method, the modified GA using variable-length integer-coded chromosome is embedded in the RFE process as each stair in the inverted triangle of GA-RFE. The embedded GA includes the following steps. First, we initialize the GA population by a certain amount of individuals representing gene combinations with the same sizes. Then, we perform fitness calculation and genetic operators including mutation, crossover, and selection until the stopping criterion is satisfied. In the end, we return the best individuals that represent the best gene combinations to GA-RFE. The stopping criterion of embedded GA is iteration time, which is set to 1 to 3.

@@

	A truncation selection method is used as the selection operator in embedded GA \cite{P37}, which simply ranks all individuals and selects the top ones to form the next generation. The elitism preservation mechanism is used to save the currently generated best individuals. The mutation and crossover operators for generating new individuals are adjusted to adapt to the variable-length integer-encoding technique. One main challenge that should be addressed in these two processes is avoidance of duplicated genes in every individual, which leads to the decline of the number of actual existing genes. Based on our encoding technique, the mutation operation for an individual is randomly changing some genes to others. It should be ensured that new genes do not exist in this individual previously to avoid repetitions. Crossover in embedded GA also involves single-point crossover which is the most widely used crossover method in binary encoding. Specifically, a random position is selected in the chromosome, and two parent individuals split themselves at this crossover point and then exchange chromosome tails to generate children individuals. After the crossover, the potential duplicate genes in the children individuals are replaced with other genes from their parents to avoid decreasing the gene number. Fitness (\(F\)) of an individual is defined in Equation (\ref{eq:2}):
	{
		\scriptsize
		\begin{eqnarray}\label{eq:2}
		F = \left\{
		\begin{array}{cl}
		Acc & {,\text{balanced\ dataset}}\\
		\alpha Acc + (1-\alpha)Avc & {,\text{imbalanced\ dataset}}\\
		\end{array} \right.
		\end{eqnarray}
	}
	, where \(\alpha\) is an adjustment coefficient to deal with the imbalanced datasets. For imbalanced datasets, fitness defined as \(\alpha Acc +(1-\alpha)Avc\) can adjust the trend of predicting samples as abundant classes for \(Avc = (Sn + Sp) \big/ 2\) takes the correct prediction proportion of both sample classes into consideration. In our experiments, we take \(\alpha\) 0.6 for imbalanced datasets. For balanced datasets, \(F\) is simply defined as \(Acc\). \(F\) is calculated by 5-fold CV, and the employed classifier is Gaussian Naive Bayes classifier (NB) \cite{P35}. We sort different GA individuals based on two metrics, \(F\) and gene number. The individual with higher \(F\) is superior. For two individuals with the same \(F\) values, the one with a smaller gene number is superior. MGRFE and GA-RFE also use the above-mentioned sorting rule to rank different gene combinations.

@@

	GA-RFE as shown in Fig. \ref {Fig:MGRFE_flowchart} is designed as an explicit recursive feature elimination process with embedded GA to find minimal discriminatory gene combinations. First, we randomly generate the initial GA population based on a certain candidate gene set and chromosome length. Then, we implement a chromosome length drop and a GA run in turns until the chromosome length in GA drops to 1. Finally, we sort the optimal gene combinations from all GA runs and then return the overall top-ranked gene combinations to MGRFE. The chromosome length drop means that every individual in the current GA population randomly discards the same number of genes to generate the new GA population for the next run. The number of discarded genes between two GA runs, the RFE step, is set from 1 to 3 according to the current chromosome length. A larger decline step is set for larger chromosome length to avoid time cost and a smaller decline step set for smaller chromosome length to do precise searching.

@@

	MGRFE is designed as a multilayer iterative feature selection method with the selection unit in each layer being GA-RFE. In every iteration layer, the GA-RFE processes analyze the current candidate gene set and return their obtained optimal gene combinations. Then the candidate gene set is reduced and subjected to the next layer of iterative selection. The candidate gene set used by the first layer of MGRFE is from the search space reduction stage. After each iteration layer, all optimal gene combinations in MGRFE will be sorted and the top-ranked ones will form the updated reduced candidate gene set. After the specified layers of iteration, MGRFE sorts all the optimal gene combinations and provides the top-ranked gene combinations for Stage 3 to execute further validation.

@@

	In this section, comprehensive experiments on total 19 datasets are performed to validate the performance of MGRFE.  
	Furthermore, the independent validation and biological verification of the selected genes are provided.

@@

	The results of MGRFE on Dataset One including 17 binary datasets are given in Table \ref{Tab:RST all index}, where six measurements calculated by 5-fold CV and the \textit{t}-test and MIC-based gene rankings are listed. For 17 datasets, \(Acc\) values are all above 0.9 within 10 genes. Moreover, for 8 of 17 datasets (DLBCL, Leuk, ALL1, Lym, Adeno, Gas, Gas2, and Stroke), \(Acc\) reached 1.0 with gene number less than 5. MGRFE also show the strong robustness in dealing with imbalanced datasets like DLBCL, Colon, Leuk, ALL1, ALL4, and CNS, for which \(Sn\), \(Sp\), \(Avc\), \(MCC\), and \(AUC\) are all above 0.95 without being influenced by the data imbalance. 
	According to the \textit{t}-test and MIC-based gene ranking, the best gene feature subset is not always the highest-ranked features in the filter method, thus the filter algorithm alone cannot generate the optimal feature combination.
	It could be noted that the relative positions of selected genes in the two ranking methods are consistent on most datasets. The top-ranked genes in the \textit{t}-test are also top-ranked in the MIC sorting (e.g. the selected gene on ALL1 is the top one in both \textit{t}-test and MIC ranking). For 5 of 17 datasets, the top one gene  according to the \textit{t}-test appeared in the final selected gene subsets. Generally, the selected informative genes are top-ranked by the \textit{t}-test and MIC methods. Therefore, the filter techniques are qualified for the search space reduction task. Moreover, MGRFE achieves relatively stable classification performance in 10 repetitions of 10-fold CV as depicted in Fig. \ref{Fig:CV1}.

@@

	McTwo \cite{W16} thoroughly tested all the datasets in Dataset One and demonstrated satisfactory performance. Here, we present the performance comparison between McTwo and MGRFE. Table \ref{Tab:CMP McTwo RST} lists the overall maximal \(Acc\) and numbers of selected genes on total 17 datasets for MGRFE and McTwo. 
	On all 17 datasets, MGRFE can obtain equal or better prediction performance compared to McTwo. 
%	For a more intuitive comparison, Fig. \ref{Fig:CMP McTwo} offers the line chart of maximal \(Acc\) achieved by the two algorithms on 17 datasets, where MGRFE obviously outperforms McTwo with a higher \(Acc\) line. 	
	On five datasets ALL2, ALL3, ALL4, Stroke and CNS, MGRFE achieves distinctly better classification performance than McTwo with relatively more genes. For a fairer and more specific comparison, the \(Acc\) values of the two algorithms are listed when the gene number of MGRFE is equal to McTwo as shown in Table \ref{Tab:same gene num}. The results indicate that MGRFE still outperforms McTwo. Nonetheless, the \(Acc\) values associated with the usage of the gene numbers fall behind our optimal \(Acc\) values on these datasets. Thus, MGRFE selected somewhat more genes to achieve the optimal results.

%	\begin{figure*}[ht]
%		\centering
%		\includegraphics[width=0.72\textwidth]{pictures/CMP-McTwo.pdf}
%		\caption{The line plots of overall maximal accuracy for MGRFE and McTwo on 17 datasets in Dataset One.}
%		\label{Fig:CMP McTwo}
%	\end{figure*}

@@

	Here we present the results of MGRFE on Dataset Two including three benchmark datasets, where two datasets are multiclass datasets. MGRFE selects five, two, and three genes in SRBCT, ALL\_AML, and MLL respectively and the overall maximal \(Acc\)s are all 1.0 in 5-fold CV. In our experiments, we notice that the \(Acc\) values of the best GA individuals are kept at 1.0 in the majority of gene number ranges and only begin to drop when the gene number is significantly reduced. We also carried out 10 repetitions of 10-fold CV to further validate the final selected gene combinations in Dataset Two as shown in Fig. \ref{Fig:CV2}. The mean of \(Acc\)s for SRBCT, ALL\_AML, and MLL are 1.0, 0.982, and 0.997, respectively, with standard deviations being 0.0, 0.008, and 0.006. The results confirm that MGRFE has high classification stability.

%	\begin{figure*}[!htbp]
%		\begin{minipage}[t]{0.3\textwidth}
%			\centering
%			\includegraphics[height=1.55in]{pictures/SRBCT-RFE.pdf}
%		\end{minipage}
%		\begin{minipage}[t]{0.3\textwidth}
%			\centering
%			\includegraphics[height=1.55in]{pictures/ALLAML-RFE.pdf}
%		\end{minipage}
%		\begin{minipage}[t]{0.3\textwidth}
%			\centering
%			\includegraphics[height=1.55in]{pictures/MLL-RFE.pdf}
%		\end{minipage}
%		\caption{Three typical GA-RFE processes on the three benchmark datasets from Dataset Two.}
%		\label{Fig:3 RFE on benchmarks}
%	\end{figure*}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.45\textwidth]{pictures/CV2.pdf}
		\caption{The distribution of $Acc$ values in 10-time 10-fold CV for the selected gene combinations in Dataset Two.}
		\label{Fig:CV2}
	\end{figure}

@@

	\begin{table*}[htbp]
		\centering
		\caption{Performance comparison among the methods on the MLL dataset}
		\label{Tab:MLL RST}
		\resizebox{0.85\textwidth}{!}{
			\begin{tabular}{lllllllllllll}
				\toprule
				Experiments & Methods & \multicolumn{4}{l}{Genes} & \multicolumn{4}{l}{CV $Acc$(\%)} & Train $Acc$(\%) & Test $Acc$(\%) \\
				\midrule
